Assessing Usability of Tor Browser

### 2015-04-10 PETS2015-paper/paper.tex
rough parts..

%\numberofauthors{1}
%\author{
% \alignauthor Anonymous\\
%   \vspace{0.5em}
%   \affaddr{Some Place}
%}
\maketitle
{\color {red} TODO: write the paper for PETS currently, it is the same as the class paper..}

@@

% A category with the (minimum) three required fields
%\category{K.6.5.}{Management of Computing and Information Systems}{Security and protection}[Unauthorized access]

%\terms{Human Factors}{Measurement}{Security}

@@

\section{What we already did/background stuff}

Text here.

>>>>

%\numberofauthors{1}
%\author{
% \alignauthor Anonymous\\
%   \vspace{0.5em}
%   \affaddr{Some Place}
%}
\maketitle

@@

@@

\section{What we already did/background stuff}
Tor is an anonymity tool which is used by a lot of people. It is important (prove this/cite stuff/say something more meaningful about this) and works well. However, there are complaints that Tor is not usable. Norcie did an experiment \cite{norcie2012eliminating} which identified stopping points in Tor browser, finding out when people would get frustrated with Tor so much they would stop using it. But what about the people who are using Tor? what usability issues would thee be if people were not stopped?

To our knowledge, that has been the only user study of Tor. Since then, Tor has a lot of updates. Additionally, there were a lot of features that were untested. We ran a small pilot study on 5 journalists which involved a cognitive walkthrough.(explain cognitive walkthrough if necessary). We did this to find new stopping points, but also to see how they would download Tor, if they could understand the address bar/menu, how well they were able to complete basic tasks (searching, setting new circuits, etc), and generally if they had any usability complaints about the browser.

Recruitment here. Demographics here. Setup here. Explain that other Tor users could see this as well. How long each the experiment took on average here. (put any misc details or additional methodology things here). The result was that people did have difficulty with X, Y, Z.
